### 2017-12-02 Paper_[2017-11]_HPC/paper.tex
I have now properly added all my relevant VarSys work to this repo under a common format. This will make my work as transferrable to another person as it can possibly be. I chunked large files so that they all fit into the repo.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,trim={0 .5in 0 .4in}]{Raw_Throughput.pdf}
  \caption{Histograms of 100-bin reductions of the PMF of I/O
    throughput mean (top) and I/O throughput sample variance
    (bottom). In the mean plot, the first 1\% bin (truncated in plot)
    has a probability mass of .45. In the variance plot, the first 1\%
    bin has a probability mass of .58. It can be seen that the
    distributions of throughputs are primarily of lower magnitude with
    occasional extreme outliers.}
  \label{fig:raw_throughput}
\end{figure}

\subsection{Dimensional Analysis}
This work utilizes an extension to standard $k$-fold cross validation
that allows for a more thorough investigation of the expected model
performance in a variety of real-world situations. Alongside
randomized splits, two extra components are considered: the amount of
training data provided, and the dimension of the input data. It is
important to consider that algorithms that perform well with less
training input also require less experimentation. Although, the amount
of training data required may change as a function of the number of
input dimensions and this needs to be studied as well. The framework
used here will be referred to as a multidimensional analysis (MDA) of
the IOzone data.

@@

\subsubsection{Multidimensional Analysis}
This procedure combines random selection of training and testing
splits with changes in the input dimension and the ratio of training
size to testing size. Given an input data matrix with $n$ rows
(points) and $d$ columns (components), MDA proceeds as follows:
\begin{enumerate}
\item for all $k = 1, \ldots, d$ and for all subsets of input
  components $F = \{ j_1, j_2, \ldots j_k \}$; reduce the input data
  to unique points $z \in \mathbb{R}^k$ with $f(z) = E[ \{ f(x^{(i)})
    \quad \forall i \quad s.t. \quad (x^{(i)}_F = z) \} ]$ where
  $x^{(i)}_F$ is the $k$-tuple containing only those components of
  $x^{(i)}$ in $F$.
\item for all $r$ in $\{5, 10, \ldots, 95\}$; generate $N$ random
  splits $(train, test)$ of the reduced data with $r$ percentage for
  training and $100 - r$ percentage for testing.
\item when generating each random $(train, test)$ split, ensure that
  all points from $test$ are on or inside the convex hull of points in
  $train$; also ensure that the points in $train$ are well spaced.
\end{enumerate}

In order to ensure that the testing points are inside the convex hull
of training points, this paper identifies the set of (reduced
dimension) points that compose the convex hull and forcibly places
those points in the training set. In order to ensure that training
points are well spaced, this paper relies on the statistical method
for picking points from \shortciteN{amos2014algorithm} that proceeds
as follows:
\begin{enumerate}
\item Generate a sequence of all pairs of points sorted by ascending
  pairwise $L_2$ distance between points, ${(x^{(i_1)},x^{(j_1)}),
    (x^{(i_2)},x^{(j_2)}), \ldots}$ such that
  $||x^{(i_k)}-x^{(j_k)}||_2 \leq ||x^{(i_{k+1})}-x^{(j_{k+1})}||_2$
\item Sequentially remove points from candidacy until only $N$ remain
  by randomly selecting one point from the pair $(x^{(i_k)},
  x^{(j_k)})$ for $k = 1,\ldots$ if both $x^{(i_k)}$ and $x^{(j_k)}$
  are still candidates.
\end{enumerate}

@@

The modeling techniques generated estimates of drastically different
quality when predicting I/O throughput mean and sample variance. A few
notable characteristics include: the SVR has the largest range of
errors for all selections of dimension and amount of training data;
MARS and LSHEP produce similar magnitude errors while the former
consistently underestimates and the latter consistently overestimates
in predictions; and Delaunay has considerably fewer outliers than all
other methods. SVR likely experiences the greatest quantity of errors
because the underlying parametric representation is global and
oversimplified (a single polynomial), making it unable to capture the
complex local behaviors of system I/O. It is still unclear however
what causes the behaviors of LSHEP, MARS, and Delaunay. An exploration
of this topic is left to future work.

@@

Finally, the ability of the models to predict variance was
significantly worse for I/O sample variance. The larger scale in
variance responses alone do not account for the increase in relative
errors witnessed. This suggests that system variability has an greater
underlying functional complexity when compared with the system mean
and that latent factors are reducing prediction performance
considerably.

@@

There remain many other multivariate modeling techniques not included
in this work that should be evaluated and applied to HPC performance
tuning. For I/O alone, there are far more than the four tunable
parameters studied in this work. Alongside experimentation with more
models, there is room for a theoretical characterisation of the
combined model and data properties that allow for the greatest
predictive power.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth,trim={0 .5in 0 .4in}]{Raw_Throughput.pdf}
  \caption{Histograms of 100-bin reductions of the PMF of I/O
    throughput mean (top) and I/O throughput sample variance
    (bottom). In the mean plot, the first 1\% bin (truncated in plot)
    has a probability mass of .45. In the variance plot, the second
    1\% bin has a probability mass of .58. It can be seen that the
    distributions of throughputs are primarily of lower magnitude with
    occasional extreme outliers.}
  \label{fig:raw_throughput}
\end{figure}

\subsection{Dimensional Analysis}
This work utilizes an extension to standard $k$-fold cross validation
that allows for a more thorough investigation of the expected model
performance in a variety of real-world situations. Alongside
randomized splits, two extra components are considered: the amount of
training data provided, and the dimension of the input data. It is
important to consider that algorithms that perform well with less
training input also require less experimentation. Although, the amount
of training data required may change as a function of the dimension of
the input and this needs to be studied as well. The framework used
here will be referred to as a multidimensional analysis (MDA) of the
IOzone data.

@@

\subsubsection{Multidimensional Analysis}
This procedure combines random selection of training and testing
splits with changes in the input dimension and the ratio of training
size to testing size. Given an input data matrix with $n$ rows
(points) and $d$ columns (components), MDA proceeds as follows:
\begin{enumerate}
\item for all $k = 1, \ldots, d$ and for all subsets of input
  components $F = \{ j_1, j_2, \ldots j_k \}$; reduce the input data
  to unique points $z \in \mathbb{R}^k$ with $f(z) = E[ \{ f(x^{(i)})
    \quad \forall i \quad s.t. \quad (x^{(i)}_F = z) \} ]$ where
  $x^{(i)}_F$ is the $k$-tuple containing only those components of
  $x^{(i)}$ in $F$.
\item for all $r$ in $\{5, 10, \ldots, 95\}$; generate $N$ random
  splits $(train, test)$ of the reduced data with $r$ percentage for
  training and $100 - r$ percentage for testing.
\item when generating each of $N$ random $(train, test)$ splits,
  ensure that all points from $test$ are on or inside the convex hull
  of points in $train$; also ensure that the points in $train$ are
  well spaced.
\end{enumerate}

In order to ensure that the testing points are inside the convex hull
of training points, this paper identifies the set of (reduced
dimension) points that compose the convex hull and forcibly places
those points in the training set. In order to ensure that training
points are well spaced, this paper relies on the statistical method
for picking points from \shortciteN{amos2014algorithm} that proceeds
as follows:
\begin{enumerate}
\item Generate a sequence of all pairs of points sorted by ascending
  pairwise $L_2$ distance between points, ${(x^{(i_1)},x^{(j_1)}),
    (x^{(i_2)},x^{(j_2)}), \ldots}$ such that
  $||x^{(i_k)}-x^{(j_k)}||_2 \leq ||x^{(i_{k+1})}-x^{(j_{k+1})}||_2$
\item Sequentially remove points from candidacy until only $|train|$
  remain by randomly selecting one point from the pair $(x^{(i_k)},
  x^{(j_k)})$ for $k = 1,\ldots$ if both $x^{(i_k)}$ and $x^{(j_k)}$
  are still candidates.
\end{enumerate}

@@

The modeling techniques generated estimates of drastically different
quality when predicting I/O throughput mean and sample variance. A few
notable characteristics include: the SVR has the largest range of
errors for all selections of dimension and amount of training data;
MARS and LSHEP produce similar magnitude errors while the former
consistently underestimates and the latter consistently overestimates
in predictions; and Delaunay has considerably fewer outliers than all
other methods. SVR likely produces the poorest quality predictions
because the underlying parametric representation is global and
oversimplified (a single polynomial), making it unable to capture the
complex local behaviors of system I/O. It is still unclear however
what causes the behaviors of LSHEP, MARS, and Delaunay. An exploration
of this topic is left to future work.

@@

Finally, the ability of the models to predict variance was
significantly worse for I/O sample variance. The larger scale in
variance responses alone do not account for the increase in relative
errors witnessed. This suggests that system variability has a greater
underlying functional complexity when compared with the system mean
and that latent factors are reducing prediction performance.

@@

There remain many other multivariate modeling techniques not included
in this work that should be evaluated and applied to HPC performance
prediction. For I/O alone, there are far more than the four tunable
parameters studied in this work. Alongside experimentation with more
models, there is room for a theoretical characterisation of the
combined model and data properties that allow for the greatest
predictive power.

### 2017-12-02 Report_[2017-06-05]_Box_Mesh_Summary/BS_Report.tex
I have now properly added all my relevant VarSys work to this repo under a common format. This will make my work as transferrable to another person as it can possibly be. I chunked large files so that they all fit into the repo.

\documentclass[11pt,margin=1in]{article}
\usepackage[margin=1in]{geometry}         % Document setup
\usepackage{graphicx}                     % Including pictures
\usepackage{amsmath}                      % Math mode
\usepackage{tikz}                         % For drawing example boxes
\usepackage{algorithm2e}                  % For including box mesh algorithm
\usetikzlibrary{shapes}                   % For the 'circle' shape
\renewcommand{\familydefault}{\sfdefault} % Setting the font

\begin{document}
\begin{center}
  \textbf{Report on Box Spline Interpolation and Approximation}\\
  May $\text{29}^\text{th}$, 2017\\
  Thomas Lux
\end{center}

>>>>

\documentclass[11pt,margin=1in]{article}
\usepackage[margin=1in]{geometry}         % Document setup
\usepackage{graphicx}                     % Including pictures
\usepackage{amsmath}                      % Math mode
\usepackage{amssymb}                      % Math mode symbols
\usepackage{tikz}                         % For drawing example boxes
\usepackage{algorithm2e}                  % For including box mesh algorithm
\usetikzlibrary{shapes}                   % For the 'circle' shape
\renewcommand{\familydefault}{\sfdefault} % Setting the font

\begin{document}

\begin{center}
  \textbf{Box Spline Mesh Algorithm Summary}\\
  June $\text{5}^\text{th}$, 2017\\
  Thomas Lux
\end{center}

Given data $N = \{x_1, x_2, \dots, x_n\}\ |\  x_i \in \mathbb{R}^d$, and
associated response values $\{y_1, y_2, \dots, y_n \}$.

\section{Construct Box Mesh}
Each box in the box mesh will be specified by a center $c \in \mathbb{R}^d$,
lower width $l \in \mathbb{R}^d$, and upper width $u \in \mathbb{R}^d$. 
A point $x_i$ is contained by a box if $(1 \leq j \leq d) (c_j - l_j < x_{i,j} < c_j + u_j)$.
A two dimensional visual example of the containment region of a box, as we refer to it:

\vspace{1mm}

The only restriction is that all widths must be greater than
zero. This means that $\text{min}_i\ l_i > 0 $ and $\text{min}_i\ u_i
> 0$. First, order the data in $N$ appropriately (discussed later),
initialize a single box with $c = x_1$ and lower and upper widths of
infinity.  Now, proceed to add the rest of the points in $N$ by:

\begin{algorithm}[H]
 \For{$i = 2, \cdots, n$}{
  Identify boxes $\mathbf{B}$ that contain $x_i$\;
  Initialize box \textit{m} with center $x_i$ that contains all boxes in $\mathbf{B}$\;
  \For{$b$ in $\mathbf{B}$}{
    split dimension := $\text{max}_j$ $|\text{b-center}_{j}-\text{m-center}_{j}|$\;
    Adjust the widths of $b$ and \textit{m} in \textit{split dimension}\\
    to be the difference between the centers in that dimension.
  }
 }
\end{algorithm}

\section{Evaluating A Box}
Interpolating and approximating requires using a set of boxes as
regions of influence for response values. Given a new data point $x$
is contained by a box $b$ (with associated $c$,$l$,and $u$), we
evaluate $b(x)$ as:

\begin{enumerate}
\item Scale $x$ according to the lower and upper widths of $b$ such
  that all $x_j < c_j$ map to $(0,0.5)$ and all $x_j > c_j$ map to
  $(0.5,1)$.
\item Scale this box-normalized $x$ to be in the appropriate range for
  the order of B-Spline chosen ($\times 2$ for order 2,$\times 3$ for order 3, etc.)
\item Take the product of the B-Splines along each dimension for the
  box spline normalized $x$ value. $\prod_{j=1}^{d} f(x_j)$ where $f$
  is the piecewise polynomial defining the b-spline of the desired order.

\end{enumerate}

\section{Interpolate $y$ for new $x$}

Identify the set of boxes $\mathbf{B} = \{b_i\ |\ b_i\ \text{contains}\ x\}$.
Calculate the estimated response value by
$$\frac{\sum_{b\in\mathbf{B}}b\text{-response} \times b(x)}{\sum_{b\in\mathbf{B}}b(x)}$$
where $b\text{-response}$ is the response value associated with each
box. Notice that this is using the box functions as a weighted sum.

\section*{Notes}

The ordering that has been used when adding points to the box mesh thus far is:

\begin{itemize}
\item Add the $x_i$ with the median valued $y_i$.
\item Compute the approximation surface error at all remaining $x_i$,
  add the $x_i$ to the surface with the most (relative) error.
\item Repeat previous step until small enough maximum error is obtained.
\end{itemize}

It is important to note that this constant recalculation of error
causes an increase in the runtime by a factor of $n$.

%===============================
%     Old Report (too long)     
%===============================
